WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-08 ThePaper.tex
x-axis, y-axis, z-axis

To overcome the issues using AKKA, we moved to the concept of container orchestration based microservice architecture. The \acrshort{wdias} used \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications. Using \acrshort{k8s}, users can add required resources as Nodes to the cluster, and K8s manage and deploy applications as pods into cluster nodes.
In next \cref{pse:wdias_architecture}, we discussed about the \acrshort{wdias} used microservice concepts such as implement microservice as dumb pipes rather implementing smart endpoints, uses database per service with access via API only, distributed Transactions over microservices using event processing, and considering distributed systems scalability in directions of X-axis scaling, Y-axis scaling and Z-axis scaling.

@@

Improve the \emph{Grid data performance} by porting \acrshort{netCDF} C or FORTRAN implementation with adapter-grid rather using a Python wrapper. Using tools like Terraform which is independent of the Cloud Computing provider \emph{define \acrshort{wdias} infrastructure as code}, then users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle. \emph{Tune \acrshort{wdias} database structure performance} with using Z-axis scaling. Some of other features are alerting extension modules, publisher subscriber capabilities via extension modules, supporting irregular Grids.

>>>>

To overcome the issues using AKKA, we moved to the concept of container orchestration based microservice architecture. The \acrshort{wdias} used \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications. Using \acrshort{k8s}, users can add required resources as Nodes to the cluster, and K8s manage and deploy applications as pods into cluster nodes.
In next \cref{pse:wdias_architecture}, we discussed about the \acrshort{wdias} used microservice concepts such as implement microservice as dumb pipes rather implementing smart endpoints, uses database per service with access via API only, distributed Transactions over microservices using event processing, and considering distributed systems scalability in directions of x-axis scaling, y-axis scaling and z-axis scaling.

@@

Improve the \emph{Grid data performance} by porting \acrshort{netCDF} C or FORTRAN implementation with adapter-grid rather using a Python wrapper. Using tools like Terraform which is independent of the Cloud Computing provider \emph{define \acrshort{wdias} infrastructure as code}, then users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle. \emph{Tune \acrshort{wdias} database structure performance} with using z-axis scaling. Some of other features are alerting extension modules, publisher subscriber capabilities via extension modules, supporting irregular Grids.

### 2020-05-08 method/sec_3-microservice.tex
x-axis, y-axis, z-axis

\paragraph{X-axis Scaling}-- When scaling an application through the X-axis, multiple instances of the application execute behind a load balancer. If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load. The above simple approach is commonly to scale a service.

\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis scaling segregates the application into multiple services in the same domain. So, the end services are responsible for one or more closely related functions of the previous service before the segregation. There are different ways to split the application into services.
\begin{itemize}
    \item Verb-based decomposition. e.g., checkout.
    \item Decompose the application by the noun. e.g., order management.
    \item It is possible to use a combination of verb-based and noun-based decomposition for an application.
\end{itemize}
\emph{The microservice architecture is an application of Y-axis scaling}.

\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling). The big difference is that each service is responsible for only a subset of the data. Z-axis splits are commonly used to scale databases. As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.

@@

Export module microservices also follow the concepts of single responsibility and provide the capability to export the data into required formats of the weather models. Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using Z-axis scaling concepts.

>>>>

\paragraph{X-axis Scaling}-- When scaling an application through the x-axis, multiple instances of the application execute behind a load balancer. If there are \textit{n} copies, then each copy handles 1/\textit{n} of the load. The above simple approach is commonly to scale a service.

\paragraph{Y-axis Scaling}-- When compared to the z-axis and x-axis scaling, which follows the concept of running multiple identical copies of the application, but y-axis scaling segregates the application into multiple services in the same domain. So, the end services are responsible for one or more closely related functions of the previous service before the segregation. There are different ways to split the application into services.
\begin{itemize}
    \item Verb-based decomposition. e.g., checkout.
    \item Decompose the application by the noun. e.g., order management.
    \item It is possible to use a combination of verb-based and noun-based decomposition for an application.
\end{itemize}
\emph{The microservice architecture is an application of y-axis scaling}.

\paragraph{Z-axis Scaling}-- The z-axis scaling follows the concept of each service running the same application code (similar to x-axis scaling). The big difference is that each service is responsible for only a subset of the data. z-axis splits are commonly used to scale databases. As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
Even our research is a design based on the y-axis scaling; it is possible to use the z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.

@@

Export module microservices also follow the concepts of single responsibility and provide the capability to export the data into required formats of the weather models. Each data type adapter follows the microservice architecture concept of database per service, as mentioned in \cref{subse:database_per_service} When the system requires more database throughput, it is easy to scale each database instance by adding more resources or using z-axis scaling concepts.

### 2020-05-08 method/sec_4-db_struct.tex
x-axis, y-axis, z-axis

Two individual instances of InfluxDB used for adapter-scalar and adapter-vector services in the \acrshort{wdias} system. For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}. If users want further performance, the database can split into another set of partitions based on other key attributes based on the Z-axis scaling described in \cref{subse:scale_cube}. As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseriesType.

@@

We used MongoDB geospatial features to support Geo queries in the \acrshort{wdias}. Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries. If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB. Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
Here we used the \emph{Y-axis scaling} concept by splitting metadata search into multiple services. Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

>>>>

Two individual instances of InfluxDB used for adapter-scalar and adapter-vector services in the \acrshort{wdias} system. For the scalability, the system uses \emph{database per service}, as mentioned in \cref{subse:database_per_service}. If users want further performance, the database can split into another set of partitions based on other key attributes based on the z-axis scaling described in \cref{subse:scale_cube}. As an example, scalar and vector adapters can further split into more services based on other key attributes such as timeseriesType.

@@

We used MongoDB geospatial features to support Geo queries in the \acrshort{wdias}. Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries. If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB. Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services. Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.
